% chktex-file 8
\chapter{New Spaces from Old}

\section*{Subspaces}\addcontentsline{toc}{section}{Subspaces}

\begin{exercise}{3.1}
	Prove that $\mathscr{T}_{S}$ is a topology on $S$.
\end{exercise}

\begin{proof}
	$\varnothing = S\cap\varnothing$, $S = S\cap X$. Therefore $\varnothing, S$ are in $\mathscr{T}_{S}$.

	Suppose ${(U_{\alpha})}_{\alpha\in A}$ is a family of elements of $\mathscr{T}_{S}$. Then for every $\alpha\in A$, there is an open subset $V_{\alpha}$ of $X$ such that $U_{\alpha} = S\cap V_{\alpha}$.
	\[
		\bigcup_{\alpha\in A}U_{\alpha} = \bigcup_{\alpha\in A}(S\cap V_{\alpha}) = S\cap \left(\bigcup_{\alpha\in A}V_{\alpha}\right)
	\]

	is in $\mathscr{T}_{S}$ because $\bigcup_{\alpha\in A}V_{\alpha}$ is an open subset of $X$.

	Suppose $U_{1}, \ldots, U_{n}$ are in $\mathscr{T}_{S}$, then there exist open subsets $V_{1}, \ldots, V_{n}$ of $X$ such that $U_{i} = S\cap V_{i}$ for $i = 1,\ldots, n$.
	\[
		\bigcap^{n}_{i=1}U_{i} = \bigcap^{n}_{i=1}(S\cap V_{i}) = S\cap \left(\bigcap^{n}_{i=1}V_{i}\right)
	\]

	is in $\mathscr{T}_{S}$ because $\bigcap^{n}_{i=1}V_{i}$ is an open subset of $X$.

	Thus $\mathscr{T}_{S}$ is a topology on $S$.
\end{proof}

\begin{exercise}{3.2}\label{exercise:3.2}
	Suppose $S$ is a subspace of $X$. Prove that a subset $B\subseteq S$ is closed in $S$ if and only if it is equal to the intersection of $S$ with some closed subset of $X$.
\end{exercise}

\begin{proof}
	$(\Rightarrow)$ Suppose $B$ is closed in $S$.

	Then $S\setminus B$ is open in $S$, so there is an open subset $U$ of $X$ such that $S\setminus B = S\cap U$.
	\[
		B = S\setminus (S\setminus B) = S\setminus (S\cap U) = (S\cap X)\setminus (S\cap U) = S\cap (X\setminus U)
	\]

	so $B$ is the intersection of $S$ and the closed subset $S\setminus U$ of $X$.

	$(\Leftarrow)$ Suppose $B$ is equal to the intersection of $S$ with some closed subset $A$ of $X$.
	\[
		S\setminus B = S\setminus (S\cap A) = (S\cap X) \setminus (S\cap A) = S\cap (X\setminus A).
	\]

	Because $A$ is closed in $X$, $X\setminus A$ is open in $X$. Therefore $S\setminus B$ is open in $S$, it follows that $B$ is closed in $S$.
\end{proof}

\begin{exercise}{3.3}
	Let $M$ be a metric space, and let $S\subseteq M$ be any subset. Show that the subspace topology on $S$ is the same as the metric topology obtained by restricting the metric of $M$ to pairs of points in $S$.
\end{exercise}

\begin{proof}
	Let $d$ be the metric on $M$ and $d_{S}$ is the metric on $S$ obtained by restricting $d$ to $S$. By the definition of open balls, if $x\in S$, we have
	\[
		B^{(d_{S})}_{r}(x) = \{ y : d(x, y) < r \text{ and } y\in S \} = B^{(d)}_{r}(x) \cap S.
	\]

	Let $\mathscr{T}_{d_{S}}$ be the metric topology restricted to $S$ and $\mathscr{T}_{S}$ be the subspace topology on $S$.

	\begin{itemize}
		\item Prove that $\mathscr{T}_{d_{S}}\subseteq \mathscr{T}_{S}$.

		      Let $U$ be an open subset of $S$ with the metric topology generated by $d_{S}$. For every $x\in U$, there is $r_{x} > 0$ such that $B^{(d_{S})}_{r_{x}}(x)\subseteq U$. Therefore $U = \bigcup_{x\in U}B^{(d_{S})}_{r_{x}}(x)$. Moreover, $B^{(d_{S})}_{r_{x}}(x) = S\cap B^{(d)}_{r_{x}}(x)$ so $U = S\cap \bigcup_{x\in U}B^{(d)}_{r_{x}}(x)$. Let $V = \bigcup_{x\in U}B^{(d)}_{r_{x}}(x)$ then $V$ is an open subset of $M$ and $U = S\cap V$, which means $U$ is an open subset of $S$ with the subspace topology.

		      Therefore $\mathscr{T}_{d_{S}}\subseteq \mathscr{T}_{S}$.

		\item Prove that $\mathscr{T}_{S}\subseteq \mathscr{T}_{d_{S}}$.

		      Let $U$ be an open subset of $S$ with the subspace topology, then there is an open subset $V$ of $M$ such that $U = S\cap V$. For every $x\in U$ (which means $x\in V$), there is an open ball $B^{(d)}_{r_{x}}(x)$ such that $x\in B^{(d)}_{r_{x}}(x)\subseteq V$. Therefore $U = \bigcup_{x\in U}(S\cap B^{(d)}_{r_{x}}(x)) = \bigcup_{x\in U}B^{(d_{S})}_{r_{x}}(x)$. So $U$ is an open subset of $S$ with the metric topology generated by $d_{S}$.

		      Therefore $\mathscr{T}_{S}\subseteq\mathscr{T}_{d_{S}}$.
	\end{itemize}

	Thus $\mathscr{T}_{S} = \mathscr{T}_{d_{S}}$, which means the subspace topology on $S$ is the same as the metric topology with the metric obtained by restricting the metric of $M$ to $S$.
\end{proof}

\begin{exercise}{3.6}
	Prove Proposition 3.5.

	Suppose $S$ is a subspace of the topological space $X$.
	\begin{enumerate}[label={(\alph*)}]
		\item If $U\subseteq S\subseteq X$, $U$ is open in $S$, and $S$ is open in $X$, then $U$ is open in $X$. The same is true with ``closed'' in place of ``open''.
		\item If $U$ is a subset of $S$ that is either open or closed in $X$, then it is also open or closed in $S$, respectively.
	\end{enumerate}
\end{exercise}

\begin{proof}
	\begin{enumerate}[label={(\alph*)}]
		\item Suppose $U$ is open in $S$, and $S$ is open in $X$.

		      Because $U$ is open in $S$, there is an open set $V$ in $X$ such that $U = S\cap V$. $S$ and $V$ are open in $X$, so $S\cap V$ is open in $X$, hence $U$ is open in $X$.

		      Suppose $U$ is closed in $S$, and $S$ is closed in $X$.

		      By Exercise~\ref{exercise:3.2}, there is a closed set $V$ in $X$ such that $U = S\cap V$. $S$ and $V$ are closed in $X$, so $S\cap V$ is closed in $X$, hence $U$ is closed in $X$.
		\item Suppose $U$ is open in $X$, then $U = S\cap U$, which implies $U$ is open in $S$, due to the definition of subspace topology.

		      Suppose $U$ is closed in $X$, then $U = S\cap U$, and by Exercise~\ref{exercise:3.2}, it follows that $U$ is closed in $S$.
	\end{enumerate}
\end{proof}

\begin{exercise}{3.7}
	Suppose $X$ is a topological space and $U\subseteq S\subseteq X$.
	\begin{enumerate}[label={(\alph*)}]
		\item Show that the closure of $U$ in $S$ is equal to $\overline{U}\cap S$.
		\item Show that the interior of $U$ in $S$ contains $\operatorname{Int}U\cap S$; give an example to show that they might not be equal.
	\end{enumerate}
\end{exercise}

\begin{proof}
	\begin{enumerate}[label={(\alph*)}]
		\item Let $W$ be a closed set in $S$ that contains $U$, then there is a closed set $V$ of $X$ such that $W = S\cap V$. Therefore $V$ is a closed set of $X$ that contains $U$, so $\overline{U}\subseteq V$. Hence $\overline{U}\cap S\subseteq S\cap V = W$. On the other hand, $\overline{U}\cap S$ is closed in $S$ and $U\subseteq \overline{U}\cap S$, so $\overline{U}\cap S$ is the smallest closed set in $S$ that contains $U$.

		      Thus the closure of $U$ in $S$ is equal to $\overline{U}\cap S$.
		\item Since $\operatorname{Int} U\subseteq U\subseteq S$, $\operatorname{Int}U\cap S\subseteq U\cap S = U$. $\operatorname{Int}U$ is open in $X$, so $\operatorname{Int} U\cap S$ is open in $S$. Hence the interior of $U$ in $S$ contains $\operatorname{Int}U\cap S$ (because the interior of a given set is the largest open set that is contained in the given set).

		      Consider $\mathbb{R}$ with the Euclidean topology. $\closedinterval{0,1}$ is closed in $\mathbb{R}$. We have $\openinterval{0, 1} = \operatorname{Int}\closedinterval{0, 1}$. The interior of $\closedinterval{0,1}$ in $\closedinterval{0,1}$ is $\closedinterval{0,1}$, however, $\operatorname{Int}\closedinterval{0,1}\cap \closedinterval{0,1} = \openinterval{0,1}$ and $\openinterval{0,1}\subsetneq\closedinterval{0,1}$. This example shows that the interior of $U$ in $S$ might not be equal to $\operatorname{Int} U\cap S$.
	\end{enumerate}
\end{proof}

\begin{exercise}{3.12}
	Prove Proposition 3.11 (Other Properties of the Subspace Topology).

	Suppose $S$ is a subspace of the topological space $X$.
	\begin{enumerate}[label={(\alph*)}]
		\item If $R\subseteq S$ is a subspace of $S$, then $R$ is a subspace of $X$; in other words, the subspace topologies that $R$ inherits from $S$ and from $X$ agree.
		\item If $\mathscr{B}$ is a basis for the topology of $X$, then
		      \[
			      \mathscr{B}_{S} = \{ B\cap S: B\in\mathscr{B} \}
		      \]

		      is a basis for the topology of $S$.
		\item If ${(p_{n})}$ is a sequence of points of $S$ and $p\in S$, then $p_{n}\to p$ if and only if $p_{n}\to p$ in $X$.
		\item Every subspace of a Hausdorff space is Hausdorff.
		\item Every subspace of a first countable space is first countable.
		\item Every subspace of a second countable space is second countable.
	\end{enumerate}
\end{exercise}

\begin{proof}
	\begin{enumerate}[label={(\alph*)}]
		\item Let $U\subseteq R$.

		      Suppose $U$ is an open set in $R$ with the topology inherited from $S$. Then there is an open set $V$ in $S$ such that $U = R\cap V$, and there is an open set $W$ in $X$ such that $V = S\cap W$. Therefore $U = (R\cap S)\cap W = R\cap W$, which means $U$ is an open set in $R$ with the topology inherits from $X$.

		      Suppose $U$ is an open set in $R$ with the topology inherited from $X$. Then there is an open set $W$ in $X$ such that $U = R\cap W$. Therefore $U = R\cap W = (R\cap S)\cap W = R\cap (S\cap W)$. Since $S\cap W$ is an open set in $S$ with topology inherited from $X$, $R\cap (S\cap W)$ is an open set in $R$ with the topology inherited from $S$.

		      Hence the topologies that $R$ inherits from $S$ and from $X$ are the same.
		\item By the definition of subspace topology, every element of $\mathscr{B}_{S}$ is open in $S$.

		      Let $U$ be an open set in $S$, then there is an open set $V$ in $X$ such that $U = S\cap V$. Because $\mathscr{B}$ is a basis for the topology of $X$, there is a collection ${(B_{i})}_{i\in I}$ of elements of $\mathscr{B}$ such that $V = \bigcup_{i\in I}B_{i}$. Therefore $U = S\cap \bigcup_{i\in I}B_{i} = \bigcup_{i\in I}(B_{i}\cap S)$. Because $U$ is an arbitrary open set in $S$ and $U$ is the union of some elements of $\mathscr{B}_{S}$, it follows that $\mathscr{B}_{S}$ is a basis for the topology of $S$.
		\item Suppose $p_{i}\to p$ in $S$.

		      Let $V$ be a neighborhood of $p$ in $X$, then $U = S\cap V$ is a neighborhood of $p$ in $S$. Because $p_{i}\to p$ in $S$, there is $N\in\mathbb{N}$ such that $p_{i}\in U$ for all $i\geq N$. Therefore $p_{i}\in V$ for all $i\geq N$, which means $p_{i}\to p$ in $X$.

		      Suppose $p_{i}\to p$ in $X$.

		      Let $U$ be a neighborhood of $p$ in $S$, then there is an open set $V$ in $X$ such that $U = S\cap V$. Because $V$ is also a neighborhood of $p$ in $X$, and $p_{i}\to p$ in $X$, there is $N\in\mathbb{N}$ such that $p_{i}\in V$ for all $i\geq N$. By the hypothesis, $p_{i}\in S$ for all $i$, so $p_{i}\in S\cap V = U$ for all $i\geq N$. Therefore $p_{i}\to p$ in $S$.
		\item Suppose $X$ is a Hausdorff space and $S$ is a subspace of $X$.

		      Let $x, y$ be two distinct points of $S$. Because $x, y$ are also points of $X$, they are separated by some neighborhoods $V_{x}, V_{y}$ in $X$. $U_{x} = S\cap V_{x}$ is a neighborhood of $x$ in $S$, $U_{y} = S\cap V_{y}$ is a neighborhood of $y$ in $S$. $V_{x}$ and $V_{y}$ are disjoint, so are $U_{x}$ and $U_{y}$, hence $x$ and $y$ are separated by open sets in $S$. Thus $S$ is Hausdorff.
		\item Suppose $X$ is a first countable space and $S$ is a subspace of $X$.

		      Let $x$ be a point of $S$ and $U$ be a neighborhood of $x$ in $S$. Let $\mathscr{B}$ be a countable neighborhood basis of $x$ in $X$. Define $\mathscr{B}_{S} = \{ S\cap B : B\in\mathscr{B} \}$. Because $U$ is open in $S$, there is an open set $V$ in $X$ such that $U = S\cap V$. Since $X$ is first countable, there is $B\in\mathscr{B}$ such that $B\subseteq V$, so $S\cap B\subseteq U\cap V = U$. Therefore $\mathscr{B}_{S}$ is a countable neighborhood basis of $x$ in $S$. Since $x$ is an arbitrary point of $S$, we conclude that $S$ is first countable.
		\item This follows directly from part (b).
	\end{enumerate}
\end{proof}

\subsection*{Topological Embeddings}\addcontentsline{toc}{subsection}{Topological Embeddings}

\begin{exercise}{3.13}
	Let $X$ be a topological space and let $S$ be a subspace of $X$. Show that the inclusion map $S\xhookrightarrow{} X$ is a topological embedding.
\end{exercise}

\begin{proof}
	Denote the inclusion map by $\iota_{S}$. If $x, y\in S$ and $x\ne y$ then $\iota_{S}(x)\ne \iota_{S}(y)$ because $\iota_{S}(x) = x, \iota_{S}(y) = y$, so $\iota_{S}$ is injective. $\iota_{S}$ is continuous, according to the characteristic property of subspace topology.

	The image set of $\iota_{S}$ is $S$. Let $f: S\to S$ defined by $f(x) = \iota_{S}(x)$, then $f$ is bijective. For every open subset $U$ of $S$, $f^{-1}(U) = U$, which is open, so $f$ is continuous. $f^{-1} = f$ so $f^{-1}$ is also continuous. Hence $\iota_{S}$ is a homeomorphism from $S$ onto its image.

	Thus the inclusion map $S\xhookrightarrow{} X$ is a topological embedding.
\end{proof}

\begin{exercise}{3.17}
	Give an example of a topological embedding that is neither an open map nor a closed map.
\end{exercise}

\begin{proof}
	Consider $\varphi: \mathbb{Q}\to \mathbb{R}$ where $\varphi(x) = x$. $\varphi$ is a topological embedding because $\mathbb{Q}$ is a subspace of $\mathbb{R}$.

	Let $A$ be a nonempty open subset of $\mathbb{Q}$, then $\varphi(A) = A$. But $A$ is not open in $\mathbb{R}$, because every neighborhood of every point of $A$ contains an irrational number. Therefore $\varphi$ is not open.

	Let $B$ be a nonempty closed subset of $\mathbb{Q}$, then $\varphi(B) = B$. $\mathbb{R}\setminus B$ is not open in $\mathbb{R}$ because every neighborhood of every point of $B$ contains a rational number, so $B$ is not closed. Therefore $\varphi$ is not closed.

	Thus $\varphi$ is a topological embedding that is neither an open map nor a closed map.
\end{proof}

\begin{exercise}{3.19}
	Prove Proposition 3.18.

	A surjective topological embedding is a homeomorphism.
\end{exercise}

\begin{proof}
	Let $\varphi: X\to Y$ be a surjective topological embedding. Because $\varphi$ is surjective, $\varphi(X) = Y$. Since $\varphi$ is a topological embedding and $\varphi(X) = Y$, $\varphi: X\to Y$ is bijective. From the definition of topological embedding, it follows that $\varphi$ is a homeomorphism.
\end{proof}

\section*{Product Spaces}\addcontentsline{toc}{section}{Product Spaces}

\begin{exercise}{3.25}
	Suppose $X_{1}, \ldots, X_{n}$ are arbitrary topological spaces. On their Cartesian product $X_{1}\times \cdots \times X_{n}$, we define the \textbf{product topology} to be the topology generated by the following basis:
	\[
		\mathscr{B} = \{ U_{1} \times \cdots \times U_{n}: \text{$U_{i}$ is an open subset of $X_{i}$, $i = 1,\ldots,n $}  \}.
	\]

	Prove that $\mathscr{B}$ is a basis for a topology.
\end{exercise}

\begin{proof}
	Every point of $X_{1}\times\cdots\times X_{n}$ is in some element of $\mathscr{B}$.

	Let $U, V\in \mathscr{B}$, then $U = U_{1}\times\cdots\times U_{n}$ and $V = V_{1}\times\cdots\times V_{n}$ for some open subsets $U_{i}, V_{i}$ of $X_{i}$, where $i = 1,\ldots,n$. Then
	\[
		U\cap V = (U_{1}\cap V_{1})\times\cdots\times (U_{n}\times V_{n})
	\]

	which means $U\cap V$ is also open in $X_{1}\times\cdots\times X_{n}$.

	Thus $\mathscr{B}$ is a basis for a topology.
\end{proof}

\begin{exercise}{3.26}
	Show that the product topology on $\mathbb{R}^{n} = \mathbb{R}\times\cdots\times\mathbb{R}$ is the same as the metric topology induced by the Euclidean distance function.
\end{exercise}

\begin{proof}
	\begin{itemize}
		\item Prove that the metric topology is coarser than the product topology on $\mathbb{R}^{n}$.

		      Let $B^{(d)}_{r}(x)$ be an open ball in $\mathbb{R}^{n}$ with the metric topology induced by the Euclidean distance function. For every $y\in B^{(d)}_{r}(x)$, consider the following open cube of $\mathbb{R}^{n}$ with the product topology:
		      \[
			      \openinterval{x_{1} - \frac{d(x, y)}{\sqrt{n}}, x_{1} + \frac{d(x, y)}{\sqrt{n}}}\times\cdots\times\openinterval{x_{n} - \frac{d(x, y)}{\sqrt{n}}, x_{n} + \frac{d(x, y)}{\sqrt{n}}}.
		      \]

		      For every point $z$ of this set
		      \[
			      d(x, z) = \sqrt{\sum^{n}_{i=1}{(x_{i} - z_{i})}^{2}} < \sqrt{\sum^{n}_{i=1}{\left(\frac{d(x, y)}{\sqrt{n}}\right)}^{2}} = d(x, y) < r.
		      \]

		      Therefore the given open cube is a subset of $B^{(d)}_{r}(x)$. Hence every open ball is an union of some open cubes, which implies every open set in $\mathbb{R}^{n}$ as a metric topology induced by the Euclidean distance function is also open in $\mathbb{R}^{n}$ with the product topology.
		\item Prove that the metric topology is finer than the product topology on $\mathbb{R}^{n}$.

		      Let
		      \[
			      R = \openinterval{a_{1},b_{1}} \times\cdots\times \openinterval{a_{n},b_{n}}
		      \]
		      be a product open set and $x\in R$. Define $r_{i} = \min\{ x_{i} - a_{i}, b_{i} - x_{i} \}$ and $r = \min\{ r_{i} : i = 1,\ldots, n \}$. For every $y\in B^{(d)}_{r}(x)$, we have
		      \begin{align*}
			      y_{i} - a_{i} & = (y_{i} - x_{i}) + (x_{i} - a_{i})                          \\
			                    & \geq -\left\vert{y_{i} - x_{i}}\right\vert + (x_{i} - a_{i}) \\
			                    & > -r + (x_{i} - a_{i})                                       \\
			                    & \geq (x_{i} - a_{i}) - r_{i}                                 \\
			                    & \geq 0
		      \end{align*}

		      and
		      \begin{align*}
			      b_{i} - y_{i} & = (b_{i} - x_{i}) + (x_{i} - y_{i})                         \\
			                    & \geq (b_{i} - x_{i}) - \left\vert{x_{i} - y_{i}}\right\vert \\
			                    & > (b_{i} - x_{i}) - r                                       \\
			                    & \geq (b_{i} - x_{i}) - r_{i}                                \\
			                    & \geq 0
		      \end{align*}

		      so $a_{i} < y_{i} < b_{i}$ for $i = 1,\ldots, n$, which implies $B^{(d)}_{r}(x)\subseteq R$.

		      Hence every product open set is open in $\mathbb{R}^{n}$ and with the metric topology induced by the Euclidean distance function. Moreover, every open set in $\mathbb{R}^{n}$ with the product topology is open in the metric topology.
	\end{itemize}

	Thus the product topology on $\mathbb{R}^{n}$ is the same as the metric topology induced by the Euclidean distance function.
\end{proof}

\begin{exercise}{3.29}
	If $X_{1}, \ldots, X_{n}$ are topological spaces, each canonical projection $\pi_{i}: X_{1}\times\cdots\times X_{n}\to X_{i}$ is continuous.

	Prove the preceding corollary using only the characteristic property of the product topology.
\end{exercise}

\begin{proof}
	The identity map $\operatorname{Id}_{X_{1}\times\cdots\times X_{n}}$ is continuous. By the characteristic property of the product topology, $\pi_{i}\circ \operatorname{Id}_{X_{1}\times\cdots\times X_{n}}$ is continuous for every $i = 1,\ldots, n$. Moreover, $\pi_{i}\circ \operatorname{Id}_{X_{1}\times\cdots\times X_{n}} = \pi_{i}$ so $\pi_{i}$ is continuous for every $i = 1,\ldots,n$.
\end{proof}

\begin{exercise}{3.32}
	Prove Proposition 3.31 (Other Properties of the Product Topology).

	Let $X_{1}, \ldots, X_{n}$ be topological spaces.
	\begin{enumerate}[label={(\alph*)}]
		\item The product topology is ``associative'' in the sense that the three topologies on
		      the set $X_{1} \times X_{2} \times X_{3}$, obtained by thinking of it as $X_{1} \times X_{2} \times X_{3}, (X_{1} \times X_{2}) \times X_{3}$, or $X_{1} \times (X_{2} \times X_{3})$ are all equal.
		\item For any $i\in\{1,\ldots,n\}$ and any points $x_{j}\in X_{j}$, $j\ne i$, the map $f: X_{i}\to X_{1}\times \cdots \times X_{n}$ given by
		      \[
			      f(x) = (x_{1}, \ldots, x_{i-1}, x, x_{i+1}, \ldots, x_{n})
		      \]

		      is a topological embedding of $X_{i}$ into the product space.
		\item Each canonical projection $\pi_{i}: X_{1}\times\cdots\times X_{n}\to X_{i}$ is an open map.
		\item If for each $i$, $\mathscr{B}_{i}$ is a basis for the topology of $X_{i}$, then the set
		      \[
			      \{ B_{1}\times\cdots\times B_{n} : B_{i}\in\mathscr{B}_{i} \}
		      \]

		      is a basis for the product topology on $X_{1}\times\cdots\times X_{n}$.
		\item If $S_{i}$ is a subspace of $X_{i}$ for $i = 1,\ldots,n$, then the product topology and the subspace topology on $S_{1}\times \cdots \times S_{n}\subseteq X_{1}\times \cdots\times X_{n}$ are equal.
		\item If each $X_{i}$ is Hausdorff, so is $X_{1}\times\cdots\times X_{n}$.
		\item If each $X_{i}$ is first countable, so is $X_{1}\times\cdots\times X_{n}$.
		\item If each $X_{i}$ is second countable, so is $X_{1}\times\cdots\times X_{n}$.
	\end{enumerate}
\end{exercise}

\begin{proof}
	\begin{enumerate}[label={(\alph*)}]
		\item Let $\operatorname{Id}_{(1,2),3}: (X_{1}\times X_{2})\times X_{3}\to X_{1}\times X_{2}\times X_{3}$ be the identity map. The following diagrams (see~\ref{fig:3.32-a-1}) commute
		      \begin{figure}[htp]
			      \renewcommand{\thefigure}{3.32-a-1}
			      \centering
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em]
				      {
					      (X_{1}\times X_{2})\times X_{3} & X_{1}\times X_{2}\times X_{3} \\
					      X_{1}\times X_{2}               & X_{1}                         \\
				      };
				      \path[->] (m-1-1) edge node[above] {$\operatorname{Id}_{(1,2),3}$} (m-1-2);
				      \path[->] (m-1-1) edge node[left] {$\pi^{(X_{1}\times X_{2})\times X_{3}}_{X_{1}\times X_{2}}$} (m-2-1);
				      \path[->] (m-2-1) edge node[below] {$\pi^{X_{1}\times X_{2}}_{X_{1}}$} (m-2-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{1}}$} (m-2-2);
			      \end{tikzpicture}
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em]
				      {
					      (X_{1}\times X_{2})\times X_{3} & X_{1}\times X_{2}\times X_{3} \\
					      X_{1}\times X_{2}               & X_{2}                         \\
				      };
				      \path[->] (m-1-1) edge node[above] {$\operatorname{Id}_{(1,2),3}$} (m-1-2);
				      \path[->] (m-1-1) edge node[left] {$\pi^{(X_{1}\times X_{2})\times X_{3}}_{X_{1}\times X_{2}}$} (m-2-1);
				      \path[->] (m-2-1) edge node[below] {$\pi^{X_{1}\times X_{2}}_{X_{2}}$} (m-2-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{2}}$} (m-2-2);
			      \end{tikzpicture}
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em]
				      {
					      (X_{1}\times X_{2})\times X_{3} & X_{1}\times X_{2}\times X_{3} \\
					                                      & X_{3}                         \\
				      };
				      \path[->] (m-1-1) edge node[above] {$\operatorname{Id}_{(1,2),3}$} (m-1-2);
				      \path[->] (m-1-1) edge node[below left] {$\pi^{(X_{1}\times X_{2})\times X_{3}}_{X_{3}}$} (m-2-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{3}}$} (m-2-2);
			      \end{tikzpicture}
			      \caption{}\label{fig:3.32-a-1}
		      \end{figure}

		      Due to the characteristic property of the product topology, and the composition of continuous maps is continuous, it follows that $\operatorname{Id}_{(1,2),3}$ is continuous.

		      Define $f: X_{1}\times X_{2}\times X_{3}\to X_{1}\times X_{2}$ by $f(x_{1}, x_{2}, x_{3}) = (x_{1}, x_{2})$. The two following diagrams (see~\ref{fig:3.32-a-2}) commute
		      \begin{figure}[htp]
			      \renewcommand{\thefigure}{3.32-a-2}
			      \centering
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times X_{2}\times X_{3} & X_{1}\times X_{2} \\
					                                    & X_{1}             \\
				      };
				      \path[->] (m-1-1) edge node[above] {$f$} (m-1-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{X_{1}\times X_{2}}_{X_{1}}$} (m-2-2);
				      \path[->] (m-1-1) edge node[below left] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{1}}$} (m-2-2);
			      \end{tikzpicture}
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times X_{2}\times X_{3} & X_{1}\times X_{2} \\
					                                    & X_{2}             \\
				      };
				      \path[->] (m-1-1) edge node[above] {$f$} (m-1-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{X_{1}\times X_{2}}_{X_{2}}$} (m-2-2);
				      \path[->] (m-1-1) edge node[below left] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{1}}$} (m-2-2);
			      \end{tikzpicture}
			      \caption{}\label{fig:3.32-a-2}
		      \end{figure}

		      By the characteristic property of the product topology, it follows that $f$ is continuous. Moreover, the two following diagrams (see~\ref{fig:3.32-a-3}) commute
		      \begin{figure}[htp]
			      \renewcommand{\thefigure}{3.32-a-3}
			      \centering
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times X_{2}\times X_{3} & (X_{1}\times X_{2})\times X_{3} \\
					                                    & X_{1} \times X_{2}              \\
				      };
				      \path[->] (m-1-1) edge node[above] {$\operatorname{Id}_{(1,2),3}^{-1}$} (m-1-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{(X_{1}\times X_{2})\times X_{3}}_{X_{1}\times X_{2}}$} (m-2-2);
				      \path[->] (m-1-1) edge node[below left] {$f$} (m-2-2);
			      \end{tikzpicture}
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times X_{2}\times X_{3} & (X_{1}\times X_{2})\times X_{3} \\
					                                    & X_{3}                           \\
				      };
				      \path[->] (m-1-1) edge node[above] {$\operatorname{Id}_{(1,2),3}^{-1}$} (m-1-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{(X_{1}\times X_{2})\times X_{3}}_{X_{3}}$} (m-2-2);
				      \path[->] (m-1-1) edge node[below left] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{3}}$} (m-2-2);
			      \end{tikzpicture}
			      \caption{}\label{fig:3.32-a-3}
		      \end{figure}

		      By the characteristic property of the product topology, it follows that $\operatorname{Id}_{(1,2),3}^{-1}$ is continuous. $\operatorname{Id}_{(1,2),3}$ is bijective and bicontinuous, so it is a homeomorphism. Hence $X_{1}\times X_{2}\times X_{3}$ and $(X_{1}\times X_{2})\times X_{3}$ are homeomorphic.

		      Let $\operatorname{Id}_{1,(2,3)}: X_{1}\times (X_{2}\times X_{3})\to X_{1}\times X_{2}\times X_{3}$ be the identity map. The following diagrams (see~\ref{fig:3.32-a-4}) commute
		      \begin{figure}[htp]
			      \renewcommand{\thefigure}{3.32-a-4}
			      \centering
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times (X_{2}\times X_{3}) & X_{1}\times X_{2} \times X_{3} \\
					      X_{1}                                                            \\
				      };
				      \path[->] (m-1-1) edge node[above] {$\operatorname{Id}_{1,(2,3)}$} (m-1-2);
				      \path[->] (m-1-1) edge node[left] {$\pi^{X_{1}\times (X_{2}\times X_{3})}_{X_{1}}$} (m-2-1);
				      \path[->] (m-1-2) edge node[below right] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{1}}$} (m-2-1);
			      \end{tikzpicture}
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times (X_{2}\times X_{3}) & X_{1}\times X_{2} \times X_{3} \\
					      X_{2}\times X_{3}               & X_{2}                          \\
				      };
				      \path[->] (m-1-1) edge node[above] {$\operatorname{Id}_{1,(2,3)}$} (m-1-2);
				      \path[->] (m-1-1) edge node[left] {$\pi^{X_{1}\times (X_{2}\times X_{3})}_{X_{2}\times X_{3}}$} (m-2-1);
				      \path[->] (m-2-1) edge node[above] {$\pi^{X_{2}\times X_{3}}_{X_{2}}$} (m-2-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{2}}$} (m-2-2);
			      \end{tikzpicture}
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times (X_{2}\times X_{3}) & X_{1}\times X_{2} \times X_{3} \\
					      X_{2}\times X_{3}               & X_{3}                          \\
				      };
				      \path[->] (m-1-1) edge node[above] {$\operatorname{Id}_{1,(2,3)}$} (m-1-2);
				      \path[->] (m-1-1) edge node[left] {$\pi^{X_{1}\times (X_{2}\times X_{3})}_{X_{2}\times X_{3}}$} (m-2-1);
				      \path[->] (m-2-1) edge node[above] {$\pi^{X_{2}\times X_{3}}_{X_{3}}$} (m-2-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{3}}$} (m-2-2);
			      \end{tikzpicture}
			      \caption{}\label{fig:3.32-a-4}
		      \end{figure}

		      By the characteristic property of the product topology, and the composition of continuous maps is continuous, it follows that $\operatorname{Id}_{1,(2,3)}$ is continuous.

		      Define the map $g: X_{1}\times X_{2}\times X_{3}\to X_{2}\times X_{3}$ by $g(x_{1}, x_{2}, x_{3}) = (x_{2}, x_{3})$. The following diagrams (see~\ref{fig:3.32-a-5}) commute
		      \begin{figure}[htp]
			      \renewcommand{\thefigure}{3.32-a-5}
			      \centering
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times X_{2} \times X_{3} & X_{2}\times X_{3} \\
					      X_{2}                                              \\
				      };
				      \path[->] (m-1-1) edge node[above] {$g$} (m-1-2);
				      \path[->] (m-1-1) edge node[left] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{2}}$} (m-2-1);
				      \path[->] (m-1-2) edge node[below right] {$\pi^{X_{2}\times X_{3}}_{X_{2}}$} (m-2-1);
			      \end{tikzpicture}
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times X_{2} \times X_{3} & X_{2}\times X_{3} \\
					      X_{3}                                              \\
				      };
				      \path[->] (m-1-1) edge node[above] {$g$} (m-1-2);
				      \path[->] (m-1-1) edge node[left] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{3}}$} (m-2-1);
				      \path[->] (m-1-2) edge node[below right] {$\pi^{X_{2}\times X_{3}}_{X_{3}}$} (m-2-1);
			      \end{tikzpicture}
			      \caption{}\label{fig:3.32-a-5}
		      \end{figure}

		      By the characteristic property of the product topology, it follows that $g$ is continuous. The following diagrams (see~\ref{fig:3.32-a-6}) commute
		      \begin{figure}[htp]
			      \renewcommand{\thefigure}{3.32-a-6}
			      \centering
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times X_{2} \times X_{3} & X_{1}\times (X_{2}\times X_{3}) \\
					                                     & X_{2}\times X_{3}               \\
				      };
				      \path[->] (m-1-1) edge node[above] {$\operatorname{Id}_{1,(2,3)}^{-1}$} (m-1-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{2}\times X_{3}}$} (m-2-2);
				      \path[->] (m-1-1) edge node[below left] {$g$} (m-2-2);
			      \end{tikzpicture}
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{1}\times X_{2} \times X_{3} & X_{1}\times (X_{2}\times X_{3}) \\
					                                     & X_{1}                           \\
				      };
				      \path[->] (m-1-1) edge node[above] {$\operatorname{Id}_{1,(2,3)}^{-1}$} (m-1-2);
				      \path[->] (m-1-2) edge node[right] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{1}}$} (m-2-2);
				      \path[->] (m-1-1) edge node[below left] {$\pi^{X_{1}\times X_{2}\times X_{3}}_{X_{1}}$} (m-2-2);
			      \end{tikzpicture}
			      \caption{}\label{fig:3.32-a-6}
		      \end{figure}

		      By the characteristic property of the product topology, it follows that $\operatorname{Id}_{1,(2,3)}^{-1}$ is continuous. Hence $\operatorname{Id}_{1,(2,3)}$ is bijective and bicontinuous, therefore it is a homeomorphism. So $X_{1}\times (X_{2}\times X_{3})$ and $X_{1}\times X_{2}\times X_{3}$ are homeomorphic.

		      Thus $X_{1}\times X_{2}\times X_{3}, (X_{1}\times X_{2})\times X_{3}, X_{1}\times (X_{2}\times X_{3})$ are homeomorphic.
		\item The image set of $f$ is $\{ x_{1} \} \times \cdots \times \{ x_{i-1} \} \times X_{i} \times \{ x_{i+1} \} \times \cdots \times \{ x_{n} \}$. So as a map from $X_{i}$ to its image set, $f$ is bijective.

		      The following diagrams commute
		      \begin{figure}[htp]
			      \centering
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{i} & \{ x_{1} \} \times \cdots \times \{ x_{i-1} \} \times X_{i} \times \{ x_{i+1} \} \times \cdots \times \{ x_{n} \} \\
					            & {\{ x_{k} \}}_{\text{where $k\ne i$}}                                                 \\
				      };
				      \path[->] (m-1-1) edge (m-1-2);
				      \path[->] (m-1-1) edge node[below left] {constant map} (m-2-2);
				      \path[->] (m-1-2) edge node[right] {constant map} (m-2-2);
			      \end{tikzpicture}
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      X_{i} & \{ x_{1} \} \times \cdots \times \{ x_{i-1} \} \times X_{i} \times \{ x_{i+1} \} \times \cdots \times \{ x_{n} \} \\
					            & X_{i}                                                                                                             \\
				      };
				      \path[->] (m-1-1) edge (m-1-2);
				      \path[->] (m-1-1) edge node[below left] {$\operatorname{Id}_{X_{i}}$} (m-2-2);
				      \path[->] (m-1-2) edge node[right] {canonical projection} (m-2-2);
			      \end{tikzpicture}
		      \end{figure}

		      It follows from the characteristic property of the product topology that $f$ is continuous.

		      On $\{ x_{1} \} \times \cdots \times \{ x_{i-1} \} \times X_{i} \times \{ x_{i+1} \} \times \cdots \times \{ x_{n} \}$, we use the subspace topology.

		      If $U\subseteq X_{i}$ is open, then
		      \begin{align*}
			      f(U) & = \{ x_{1} \} \times \cdots \times \{ x_{i-1} \} \times U \times \{ x_{i+1} \} \times \cdots \times \{ x_{n} \}                    \\
			           & = \left( \{ x_{1} \} \times \cdots \times \{ x_{i-1} \} \times X_{i} \times \{ x_{i+1} \} \times \cdots \times \{ x_{n} \} \right) \\
			           & \cap (X_{1}\times\cdots \times X_{i-1}\times U\times X_{i+1}\times \cdots \times X_{n}).
		      \end{align*}

		      So $f(U)$ is open in $\{ x_{1} \} \times \cdots \times \{ x_{i-1} \} \times X_{i} \times \{ x_{i+1} \} \times \cdots \times \{ x_{n} \}$.

		      Hence $f: X_{i}\to \{ x_{1} \} \times \cdots \times \{ x_{i-1} \} \times X_{i} \times \{ x_{i+1} \} \times \cdots \times \{ x_{n} \}$ is bijective, continuous, and open, so it is a homeomorphism. Thus $f$ is a topological embedding.
		\item Let $U$ be an open map in $X_{1}\times\cdots\times X_{n}$, then $U$ is an union of product open sets in $X_{1}\times\cdots\times X_{n}$. Moreover, the image of an (arbitrary) union is the union of images, in other words, $f(\bigcup_{i\in I}A_{i}) = \bigcup_{i\in I}f(A_{i})$. Then it suffices to prove that the image of a product open set is open. Let $U_{1}\times\cdots \times U_{n}$ be a product open set in $X_{1}\times \cdots\times X_{n}$, then $\pi_{i}(U_{1}\times \cdots\times U_{n}) = U_{i}$, which is open in $X_{i}$. Thus $\pi_{i}$ is an open map, for every $i = 1,\ldots,n$.
		\item Let $\mathscr{B} = \{ B_{1}\times\cdots\times B_{n} : B_{i}\in\mathscr{B}_{i} \}$, then every element of $\mathscr{B}$ is open in $X_{1}\times \cdots \times X_{n}$.

		      Every open set in $X_{1}\times\cdots\times X_{n}$ is an union of product open sets. Let $U$ is a nonempty open set in $X_{1}\times\cdots\times X_{n}$. If $(x_{1}, \ldots, x_{n})\in U$ then there exist $U_{1}\times \cdots\times U_{n}$ such that $U_{i}$ is open in $X_{i}$ for $i = 1,\ldots,n$, and $(x_{1}, \ldots, x_{n})\in U_{1}\times\cdots\times U_{n}$ (because $U$ is an union of product open sets). $\mathscr{B}_{i}$ is a basis for the topology on $X_{i}$, so there is $B_{i}\in\mathscr{B}_{i}$ such that $x_{i}\in B_{i}\subseteq U_{i}$ for $i = 1,\ldots,n$. Hence $(x_{1}, \ldots, x_{n})\in B_{1}\times\cdots\times B_{n} \subseteq U_{1}\times\cdots\times U_{n} \subseteq U$.

		      Thus $\mathscr{B}$ is a basis for the product topology on $X_{1}\times\cdots\times X_{n}$.
		\item Let ${(S_{1}\times \cdots \times S_{n})}_{s}$ be $S_{1}\times \cdots \times S_{n}$ with the subspace topology and ${(S_{1}\times \cdots \times S_{n})}_{p}$ be $S_{1}\times\cdots\times S_{n}$ with the product topology.

		      For every $i=1,\ldots,n$, define $f_{i}: {(S_{1}\times\cdots\times S_{n})}_{s}\to S_{i}$ by $f(x_{1}, \ldots, x_{n}) = x_{i}$. Let $\operatorname{Id}_{ps}: {(S_{1}\times\cdots S_{n})}_{p} \to {(S_{1}\times\cdots\times S_{n})}_{s}$ be the identity map. The following diagram (see~\ref{fig:3.32-e-1}) commutes.
		      \begin{figure}[htp]
			      \renewcommand{\thefigure}{3.32-e-1}
			      \centering
			      \begin{tikzpicture}[every edge/.style = {draw, -latex, thick}]
				      \matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
					      {(S_{1}\times\cdots\times S_{n})}_{p} & {(S_{1}\times\cdots\times S_{n})}_{s} & X_{1}\times\cdots\times X_{n} \\
					                                                                                                & S_{i}                                                                                     & X_{i}                         \\
				      };
				      \path[->] (m-1-1) edge node[below] {$\operatorname{Id}_{ps}$} (m-1-2);
				      \path[right hook->] (m-1-2) edge node[below] {$\iota_{Ss}$} (m-1-3);
				      \path[->] (m-1-3) edge node[right] {$\pi^{X_{1}\times\cdots\times X_{n}}_{X_{i}}$} (m-2-3);
				      \path[->] (m-1-2) edge node[right] {$f_{i}$} (m-2-2);
				      \path[right hook->] (m-2-2) edge node[below] {$\iota_{S_{i}}$} (m-2-3);
				      \path[->] (m-1-1) edge node[below left] {$\pi^{{(S_{1}\times\cdots\times S_{n})}_{p}}_{S_{i}}$} (m-2-2);
				      \path[->] (m-1-2) edge [bend right=45] node[below] {$\operatorname{Id}_{ps}^{-1}$} (m-1-1);
				      \path[->] (m-1-1) edge [bend left=60] node[below] {$\iota_{Sp}$} (m-1-3);
			      \end{tikzpicture}
			      \caption{}\label{fig:3.32-e-1}
		      \end{figure}

		      For every $i=1,\ldots,n$, $\iota_{S_{p}}\circ \pi^{X_{1}\times\cdots\times X_{n}}_{X_{i}} = \iota_{S_{i}}\circ \pi^{{(S_{1}\times\cdots\times S_{n})}_{p}}_{S_{i}}$, and $\pi^{{(S_{1}\times\cdots\times S_{n})}_{p}}_{S_{i}}, \iota_{S_{i}}, \pi^{X_{1}\times\cdots\times X_{n}}_{X_{i}}$ are continuous. By the characteristic property of the product topology, it follows that $\iota_{S_{p}}$ is continuous. On the other hand, $\iota_{Ss}\circ \operatorname{Id}_{ps} = \iota_{Sp}$ is continuous, so by the characteristic property of the subspace topology, it follows that $\operatorname{Id}_{ps}$ is continuous.

		      For every $i=1,\ldots,n$, $\pi^{X_{1}\times\cdots\times X_{n}}_{X_{i}}\circ \iota_{Ss} = \iota_{S_{i}}\circ f_{i}$, and $\pi^{X_{1}\times\cdots\times X_{n}}_{X_{i}}, \iota_{Ss}, \iota_{S_{i}}$ are continuous. By the characteristic property of the subspace topology, it follows that $f_{i}$ is continuous for every $i=1,\ldots,n$. Therefore, for every $i=1,\ldots,n$, $f_{i} = \pi^{{(S_{1}\times\cdots\times S_{n})}_{p}}_{S_{i}}\circ \operatorname{Id}_{ps}^{-1}$ is continuous, so by the characteristic property of the product topology, it follows that $\operatorname{Id}^{-1}_{ps}$ is continuous.

		      Hence $\operatorname{Id}_{ps}$ is bijective and bicontinuous, which means it is a homeomorphism. Thus ${(S_{1}\times\cdots\times S_{n})}_{p}$ and ${(S_{1}\times\cdots\times S_{n})}_{s}$ are homeomorphic, so the product topology and the subspace topology on $S_{1}\times\cdots\times S_{n}\subseteq X_{1}\times\cdots\times X_{n}$ are equal.
		\item Let $(x_{1}, \ldots, x_{n})$ and $(y_{1}, \ldots, y_{n})$ be two distinct points of $X_{1}\times \cdots\times X_{n}$. Because they are distinct, there is at least an index $k$ such that $x_{k}\ne y_{k}$. Since $X_{k}$ is Hausdorff, $x_{k}$ and $y_{k}$ are separated by two neighborhoods $U_{k}$ and $V_{k}$. Moreover, $X_{1}\times\cdots \times U_{k}\times\cdots\times X_{n}$ is a neighborhood of $(x_{1}, \ldots, x_{n})$, $X_{1}\times\cdots \times V_{k}\times\cdots\times X_{n}$ is a neighborhood of $(y_{1}, \ldots, y_{n})$ and
		      \[
			      (X_{1}\times\cdots \times U_{k}\times\cdots\times X_{n}) \cap (X_{1}\times\cdots \times V_{k}\times\cdots\times X_{n}) = X_{1}\times\cdots \times \varnothing\times\cdots\times X_{n} = \varnothing
		      \]

		      so $(x_{1}, \ldots, x_{n})$ and $(y_{1}, \ldots, y_{n})$ are separated by some of their neighborhoods. Because the two distinct points are arbitrary, we conclude that $X_{1}\times\cdots\times X_{n}$ is Hausdorff.
		\item Let $(x_{1}, \ldots, x_{n})$ be a point of $X_{1}\times\cdots\times X_{n}$ and $U$ be a neighborhood of $(x_{1}, \ldots, x_{n})$. Because $U$ is open in $X_{1}\times\cdots\times X_{n}$, there are open sets $U_{i}\subseteq X_{i}$ such that $(x_{1}, \ldots, x_{n})\in U_{1}\times\cdots\times U_{n}\subseteq U$. Let $\mathscr{B}_{x_{i}}$ be a countable neighborhood basis of $x_{i}$ in $X_{i}$ (the existence of such a basis is guaranteed by first countablility of $X_{i}$). Because $X_{i}$ is first countable and $U_{i}$ is a neighborhood of $x_{i}$, there is $B_{i}\in \mathscr{B}_{x_{i}}$ such that $x_{i}\in B_{i}\subseteq U_{i}$. Therefore $(x_{1}, \ldots, x_{n})\in B_{1}\times\cdots\times B_{n}\subseteq U_{1}\times\cdots\times U_{n}\subseteq U$. So the set $\{ B_{1}\times\cdots\times B_{n}: B_{i}\in\mathscr{B}_{x_{i}} \} = \mathscr{B}_{x_{1}}\times\cdots\times\mathscr{B}_{x_{n}}$ is a neighborhood basis of $(x_{1}, \ldots, x_{n})$ in $X_{1}\times\cdots\times X_{n}$. On the other hand, the Cartesian product of finitely many countable sets is countable, so $\mathscr{B}_{x_{1}}\times\cdots\times\mathscr{B}_{x_{n}}$ is countable. Thus $X_{1}\times\cdots\times X_{n}$ is first countable.
		\item For every $i=1,\ldots,n$, let $\mathscr{B}_{i}$ be a countable basis of $X_{i}$ (it exists because $X_{i}$ is second countable). It follows from part (d) that $\mathscr{B}_{1}\times\cdots\times \mathscr{B}_{n}$ is a basis for the product topology on $X_{1}\times\cdots\times X_{n}$. Because the Cartesian product of finitely many countable sets is countable, we conclude that $\mathscr{B}_{1}\times\cdots\times \mathscr{B}_{n}$ is countable. Hence $X_{1}\times\cdots\times X_{n}$ is second countable.
	\end{enumerate}
\end{proof}

\begin{exercise}{3.34}
	Suppose $f_{1}, f_{2}: X\to \mathbb{R}$ are continuous functions. Their \textbf{pointwise sum} $f_{1} + f_{2}: X\to \mathbb{R}$ and \textbf{pointwise product} $f_{1}f_{2}: X\to \mathbb{R}$ are real-valued functions defined by
	\[
		(f_{1} + f_{2})(x) = f_{1}(x) + f_{2}(x)\qquad (f_{1}f_{2})(x) = f_{1}(x)f_{2}(x).
	\]

	Pointwise sums and products of complex-valued functions are defined similarly. Use the characteristic property of the product topology to show that pointwise sums and products of real-valued or complex-valued continuous functions are continuous.
\end{exercise}

\begin{proof}
	Denote by $\mathbb{F}$ the real field $\mathbb{R}$ or the complex field $\mathbb{C}$.

	\begin{figure}[htp]
		\renewcommand{\thefigure}{3.34-1}
		\centering
		\begin{tikzpicture}[every edge/.style={draw, -latex, thick}]
			\matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
				X & \mathbb{F}\times \mathbb{F} & \mathbb{F} \\
				  & \mathbb{F}                  & \mathbb{F} \\
			};
			\path[->] (m-1-1) edge node[above] {$f$} (m-1-2);
			\path[->] (m-1-2) edge node[right] {$\pi_{1}$} (m-2-2);
			\path[->] (m-1-2) edge node[above] {$+$} (m-1-3);
			\path[->] (m-1-2) edge node[above right] {$\pi_{2}$} (m-2-3);
			\path[->] (m-1-1) edge node[below left] {$f_{1}$} (m-2-2);
			\path[->] (m-1-1) edge [bend right=90] node[below left] {$f_{2}$} (m-2-3);
		\end{tikzpicture}
		\begin{tikzpicture}[every edge/.style={draw, -latex, thick}]
			\matrix (m) [matrix of math nodes, row sep=3em, column sep=3em] {
				X & \mathbb{F}\times \mathbb{F} & \mathbb{F} \\
				  & \mathbb{F}                  & \mathbb{F} \\
			};
			\path[->] (m-1-1) edge node[above] {$f$} (m-1-2);
			\path[->] (m-1-2) edge node[right] {$\pi_{1}$} (m-2-2);
			\path[->] (m-1-2) edge node[above] {$\cdot$} (m-1-3);
			\path[->] (m-1-2) edge node[above right] {$\pi_{2}$} (m-2-3);
			\path[->] (m-1-1) edge node[below left] {$f_{1}$} (m-2-2);
			\path[->] (m-1-1) edge [bend right=90] node[below left] {$f_{2}$} (m-2-3);
		\end{tikzpicture}
		\caption{}\label{fig:3.34-1}
	\end{figure}

	The product map $f_{1}\times f_{2}: X\times X\to \mathbb{F}^{2}$ defined by $f_{1}\times f_{2}(x, y) = (f_{1}(x), f_{2}(y))$ is continuous. Define $f: X\to \mathbb{F}\times\mathbb{F}$ by $f(x) = (f_{1}(x), f_{2}(x))$, then the following diagrams (see~\ref{fig:3.34-1}) commute.

	Because $f_{1}, f_{2}$ are continuous, it follows from the characteristic property of the product topology that $f$ is continuous. The maps $+: \mathbb{F}\times\mathbb{F}\to \mathbb{F}$ and $\cdot: \mathbb{F}\times\mathbb{F}\to \mathbb{F}$ are continuous. Therefore $f_{1} + f_{2} = +\circ f$ and $f_{1}f_{2} = \cdot\circ f$ are continuous. Thus the pointwise sum and pointwise product of continuous real-valued (similarly, complex-valued) functions are continuous.
\end{proof}

\subsection*{Infinite Product}\addcontentsline{toc}{subsection}{Infinite Product}

\begin{exercise}{3.38}
	Prove Theorem 3.37 (Characteristic Property of Infinite Product Spaces).

	Let ${(X_{\alpha})}_{\alpha\in A}$ be an indexed family of topological spaces. For any topological space $Y$, a map $f: Y\to \prod_{\alpha\in A}X_{\alpha}$ is continuous if and only if each of its component functions $f_{\alpha} = \pi_{\alpha}\circ f$ is continuous. The product topology is the unique topology on $\prod_{\alpha\in A}X_{\alpha}$ that satisfies this property.
\end{exercise}

\begin{proof}
	$(\Rightarrow)$ Suppose $f$ is continuous.

	Let $U_{\alpha}$ be an open set in $X_{\alpha}$. We have ${(\pi_{\alpha}\circ f)}^{-1}(U_{\alpha}) = f^{-1}(\pi_{\alpha}^{-1}(U_{\alpha}))$. On the other hand, $\pi_{\alpha}^{-1}(U_{\alpha}) = \prod_{i\in A}Y_{i}$ where $Y_{i} = X_{i}$ if $i\ne\alpha$ and $Y_{i} = U_{i}$ if $i = \alpha$. By the definition of infinite product topology, $\prod_{i\in A}Y_{i}$ is open. Because $f$ is continuous, $f^{-1}(\pi_{\alpha}^{-1}(U_{\alpha})) = f^{-1}\left(\prod_{i\in A}Y_{i}\right)$ is open. Therefore $f_{\alpha} = \pi_{\alpha}\circ f$ is continuous for every $\alpha\in A$.

	$(\Leftarrow)$ Suppose $f_{\alpha} = \pi_{\alpha}\circ f$ is continuous for every $\alpha\in A$.

	Let $U$ be an open set of $\prod_{\alpha\in A}X_{\alpha}$. By the definition of infinite product topology, $U$ is an union of product open sets. We need to show that $f^{-1}(U)$ is open in $Y$. However, since the preimage of an arbitrary union is the union of the preimage, so it suffices to prove for the case $U$ is a product set. Let $U = \prod_{\alpha\in A}U_{\alpha}$ where $U_{\alpha} = X_{\alpha}$ for all but finitely many $\alpha\in A$. Let $A'$ be the set of elements $\alpha\in A$ such that $U_{\alpha}\ne X_{\alpha}$, then $A'$ is finite.
	\begin{align*}
		f^{-1}\left(\prod_{\alpha\in A}U_{\alpha}\right) & = f^{-1}\left(\bigcap_{\alpha\in A'}\prod_{i\in A}W_{\alpha, i}\right) \\
		                                                 & = \bigcap_{\alpha\in A'}f^{-1}\left(\prod_{i\in A}W_{\alpha,i}\right)  \\
		                                                 & = \bigcap_{\alpha\in A'}f^{-1}(\pi_{\alpha}^{-1}(U_{\alpha}))          \\
		                                                 & = \bigcap_{\alpha\in A'}{(\pi_{\alpha}\circ f)}^{-1}(U_{\alpha})
	\end{align*}

	where $W_{\alpha, i} = U_{\alpha}$ if $\alpha = i$, $W_{\alpha, i} = X_{\alpha}$ if $\alpha\ne i$. Because $A'$ is finite and ${(\pi_{\alpha}\circ f)}^{-1}(U_{\alpha})$ is open for every $\alpha\in A'$, it follows that $\bigcap_{\alpha\in A'}{(\pi_{\alpha}\circ f)}^{-1}(U_{\alpha})$ is open. Hence $f^{-1}(U)$ is open, so $f$ is continuous.

	\bigskip
	Let $X$ be $\prod_{\alpha\in A}X_{\alpha}$ with the product topology. Let $X'$ be $\prod_{\alpha\in A}X_{\alpha}$ with a topology satisfying the characteristic property. Let $\operatorname{Id}_{X,X'}: X\to X'$ be the identity map. By the characteristic property of infinite product topology, it follows that $\operatorname{Id}_{X,X'}$ and $\operatorname{Id}_{X,X'}^{-1}$ are continuous. Moreover, $\operatorname{Id}_{X,X'}$ is bijective, so $\operatorname{Id}_{X,X'}$ is a homeomorphism. Thus $X$ and $X'$ are equal, which means the product topology on $\prod_{\alpha\in A}X_{\alpha}$ is the only topology satisfying the characteristic property.
\end{proof}

\section*{Disjoint Union Spaces}\addcontentsline{toc}{section}{Disjoint Union Spaces}

\begin{exercise}{3.40}
	Show that the disjoint union topology is indeed a topology.
\end{exercise}

\begin{proof}
	Let ${(X_{\alpha})}_{\alpha\in A}$ be an indexed family of nonempty sets.

	$\varnothing, \coprod_{\alpha\in A}X_{\alpha}$ are open by definition.

	Let ${(U_{i})}_{i\in I}$ be an indexed family of subsets of the disjoint union $\coprod_{\alpha\in A}X_{\alpha}$ where $U_{i}\cap X_{\alpha}$ is open in $X_{\alpha}$ for every $i\in I, \alpha\in A$. For every $\alpha\in A$, the set
	\[
		X_{\alpha}\cap \left(\bigcup_{i\in I}U_{i}\right) = \bigcup_{i\in I}(X_{\alpha}\cap U_{i})
	\]

	is open in $X_{\alpha}$. So $\bigcup_{i\in I}U_{i}$ is open.

	Let $U_{1}, \ldots, U_{n}$ be open sets in $\coprod_{\alpha\in A}X_{\alpha}$. If $n = 0$, $\bigcap^{n}_{j=1}U_{j} = \coprod_{\alpha\in A}X_{\alpha}$. If $n > 0$
	\[
		X_{\alpha}\cap \left(\bigcap^{n}_{j=1}U_{j}\right) = \bigcap^{n}_{j=1}(X_{\alpha}\cap U_{j})
	\]

	is open in $X_{\alpha}$ for every $\alpha\in A$. Thus the disjoint union topology is indeed a topology.
\end{proof}

\begin{exercise}{3.43}\label{exercise:3.43}
	Prove Proposition 3.42 (Other Properties of Disjoint Union Spaces).

	Let ${(X_{\alpha})}_{\alpha\in A}$ be an indexed family of topological spaces.
	\begin{enumerate}[label={(\alph*)}]
		\item A subset of $\coprod_{\alpha\in A}X_{\alpha}$ is closed if and only if its intersection with each $X_{\alpha}$ is closed.
		\item Each canonical injection $\iota_{\alpha}: X_{\alpha}\to \coprod_{\alpha\in A}X_{\alpha}$ is a topological embedding and an open and closed map.
		\item If each $X_{\alpha}$ is Hausdorff, then so is $\coprod_{\alpha\in A}X_{\alpha}$.
		\item If each $X_{\alpha}$ is first countable, then so is $\coprod_{\alpha\in A}X_{\alpha}$.
		\item If each $X_{\alpha}$ is second countable and the index set $A$ is countable, then $\coprod_{\alpha\in A}X_{\alpha}$ is second countable.
	\end{enumerate}
\end{exercise}

\begin{proof}
	\begin{enumerate}[label={(\alph*)}]
		\item Let $G$ be a subset of $\coprod_{\alpha\in A}X_{\alpha}$, then its complement $\left(\coprod_{\alpha\in A}X_{\alpha}\right)\setminus G$ is $\coprod_{\alpha\in A}X_{\alpha}$. For every $\alpha\in A$, $X_{\alpha}\cap \left(\left(\coprod_{\alpha\in A}X_{\alpha}\right)\setminus G\right) = X_{\alpha}\setminus (X_{\alpha}\cap G)$.

		      $G$ is closed if and only if its complement is open. The complement of $G$ is open if and only if $X_{\alpha}\setminus (X_{\alpha}\cap G)$ is open in $X_{\alpha}$ for each $\alpha\in A$. Equivalently, the complement of $G$ is open if and only if $X_{\alpha}\cap G$ is closed in $X_{\alpha}$ for each $\alpha\in A$.

		      Thus $G\subseteq \coprod_{\alpha\in A}X_{\alpha}$ is closed if and only if its intersection with $X_{\alpha}$ is closed in $X_{\alpha}$ for each $\alpha\in A$.
		\item The image set of $\iota_{\alpha}$ is $\iota_{\alpha}(X_{\alpha}) = X_{\alpha}^{*} = X_{\alpha}$. So as a map from $X_{\alpha}$ to its image set, $\iota_{\alpha}$ is bijective. Let $V$ be an open subset of $\coprod_{\alpha\in A}X_{\alpha}$, then $\iota_{\alpha}^{-1}(V) = V\cap X_{\alpha}$, which is open in $X_{\alpha}$ (due to the definition of disjoint union topology), so $\iota_{\alpha}$ is continuous. Moreover, for every $U\subseteq X_{\alpha}$, $\iota_{\alpha}(U)\cap X_{\alpha}^{*} = \iota_{\alpha}(U)$ (which is open/closed in $X_{\alpha}$ if $U$ is open/closed in $X_{\alpha}$), and $\iota_{\alpha}(U)\cap X^{*}_{i} = \varnothing$ if $i\ne \alpha$ (which is open and closed in $X_{i}$). For each $\alpha\in A$, $X_{\alpha}$ is both open and closed in $\coprod_{\alpha\in A}X_{\alpha}$. So if $U$ is open/closed in $X_{\alpha}$, $\iota_{\alpha}(U)$ is open/closed in $\coprod_{\alpha\in A}X_{\alpha}$. Thus $\iota_{\alpha}: X_{\alpha}\to \coprod_{\alpha\in A}X_{\alpha}$ is a topological embedding, an open and closed map.
		\item Let $x, y$ be distinct points of $\coprod_{\alpha\in A}X_{\alpha}$. If $x, y$ are in the same $X_{\alpha}$, then $x, y$ are separated by some of their neighborhoods in $X_{\alpha}$ because $X_{\alpha}$ is Hausdorff. If $x\in X_{i}$ and $y\in X_{j}$ and $i\ne j$ then $x$ and $y$ are separated by $X_{i}$ and $X_{j}$. Therefore $\coprod_{\alpha\in A}X_{\alpha}$ is Hausdorff.
		\item Let $x$ be a point of $\coprod_{\alpha\in A}X_{\alpha}$, then there is $\alpha\in A$ such that $x\in X_{\alpha}$. Let $\mathscr{B}_{x}$ be a countable neighborhood basis of $x$ in $X_{\alpha}$ (such a neighborhood basis exists because $X_{\alpha}$ is first countable) and $U$ is a neighborhood of $x$ in $\coprod_{\alpha\in A}X_{\alpha}$, then $X_{\alpha}\cap U$ is a neighborhood of $x$ in $X_{\alpha}$. Since $\mathscr{B}_{x}$ is a countable neighborhood basis of $x$ in $X_{\alpha}$, then $U$ contains an element of $\mathscr{B}_{x}$. Hence $\mathscr{B}_{x}$ is also a countable neighborhood basis of $x$ in $\coprod_{\alpha\in A}X_{\alpha}$, so $\coprod_{\alpha\in A}X_{\alpha}$ is first countable.
		\item For each $\alpha\in A$, let $\mathscr{B}_{\alpha}$ be a countable basis for $X_{\alpha}$ and $\mathscr{B} = \bigcup_{\alpha\in A}\mathscr{B}_{\alpha}$. Let $U$ be an open subset of $\coprod_{\alpha\in A}X_{\alpha}$. We have $U = \bigcup_{\alpha\in A}(U\cap X_{\alpha})$, because $U\cap X_{\alpha}$ is open in $X_{\alpha}$, it is an union of elements of $\mathscr{B}_{\alpha}$, for each $\alpha\in A$. Therefore $U$ is an union of elements of $\mathscr{B}$, so $\mathscr{B}$ is a basis for the disjoint union topology on $\coprod_{\alpha\in A}X_{\alpha}$. $\mathscr{B}$ is a countable union of countable sets, so it is countable. Thus $\coprod_{\alpha\in A}X_{\alpha}$ is second countable.
	\end{enumerate}
\end{proof}

\begin{exercise}{3.44}
	Suppose ${(X_{\alpha})}_{\alpha\in A}$ is an indexed family of nonempty $n$-manifolds. Show that the disjoint union $\coprod_{\alpha\in A}X_{\alpha}$ is an $n$-manifold if and only if $A$ is countable.
\end{exercise}

\begin{proof}
	$(\Rightarrow)$ Suppose $A$ is countable.

	According to Exercise~\ref{exercise:3.43} (c) and (e), $\coprod_{\alpha\in A}X_{\alpha}$ is Hausdorff and second countable. Let $x$ be a point of $\coprod_{\alpha\in A}X_{\alpha}$ then there is $\alpha\in A$ such that $x\in X_{\alpha}$. Because $X_{\alpha}$ is an $n$-manifolds, there is a neighborhood of $x$ in $X_{\alpha}$ which is homeomorphic to $\mathbb{R}^{n}$. Because the canonical injection $\iota_{\alpha}: X_{\alpha}\to \coprod_{\alpha\in A}X_{\alpha}$ is a topological embedding, an open map, there is a neighborhood of $x$ in $\coprod_{\alpha\in A}X_{\alpha}$ which is homeomorphic to $\mathbb{R}^{n}$. Thus $\coprod_{\alpha\in A}X_{\alpha}$ is an $n$-manifold.

	$(\Leftarrow)$ Suppose $A$ is not countable.

	Let $\mathscr{B}$ be a basis for the disjoint union topology on $\coprod_{\alpha\in A}X_{\alpha}$. For each $\alpha\in A$, there is $B_{\alpha}\in\mathscr{B}$ such that $B_{\alpha}\subseteq X_{\alpha}$. Because $A$ is not countable, ${\{ B_{\alpha}: \alpha\in A \}}$ is not countable. Moreover, ${\{ B_{\alpha}: \alpha\in A \}}\subseteq \mathscr{B}$, so the basis $\mathscr{B}$ is not countable, which implies that $\coprod_{\alpha\in A}X_{\alpha}$ is not second countable. Hence $\coprod_{\alpha\in A}X_{\alpha}$ is not an $n$-manifold.

	Thus the disjoint union $\coprod_{\alpha\in A}X_{\alpha}$ is an $n$-manifold if and only if $A$ is countable.
\end{proof}

\begin{exercise}{3.45}
	Let $X$ be any space and $Y$ be a discrete space. Show that the Cartesian product $X\times Y$ is equal to the disjoint union $\coprod_{y\in Y}X$, and the product topology is the same as the disjoint union topology.
\end{exercise}

\begin{proof}
	By definition, $X\times Y$ is the set of ordered pairs $(x, y)$ where $x\in X, y\in Y$. Also by definition, $\coprod_{y\in Y}X = \{ (x, y): x\in X \land y\in Y \}$. Hence $X\times Y$ is equal to the disjoint union $\coprod_{y\in Y}X$.

	Let $U$ be an open subset of $\coprod_{y\in Y}X = \bigcup_{y\in Y}(X\times\{y\})$, then $U = \bigcup_{y\in Y}(U_{y}\times \{ y \})$ for some $U_{y}\subseteq X$ is open for each $y\in Y$. Because $Y$ is a discrete space, $\{y\}$ is open for every $y\in Y$. On the other hand, $U_{y}\times\{y\}$ is a product open set for each $y\in Y$, so $U$ is open in $X\times Y$. So the product topology is finer than the disjoint union topology.

	Let $V$ be an open subset of $X\times Y$ then $V$ is an union of product open sets. Let $U_{x}\times W_{y}$ be a product open set in that union. $U_{x}\times W_{y} = \bigcup_{y\in W_{y}}(U_{x}\times\{y\})$ so $U_{x}\times W_{y}$ is open in $\coprod_{y\in Y}X$. Hence $V$ is open in $\coprod_{y\in Y}X$. So the disjoint union topology is finer than the product topology.

	Thus the product topology on $X\times Y$ and the disjoint union topology on $\coprod_{y\in Y}X$ are the same.
\end{proof}

\section*{Quotient Spaces}\addcontentsline{toc}{section}{Quotient Spaces}

\begin{exercise}{3.46}
	Show that the quotient topology is indeed a topology.
\end{exercise}

\begin{proof}
	Let $q: X\to Y$ be a surjective map and $\mathscr{T}$ be a collection of subsets of $Y$ where $V\in\mathscr{T}$ if and only if $q^{-1}(V)$ is open in $X$.

	$q^{-1}(\varnothing) = \varnothing$ and $q^{-1}(Y) = X$ so $\varnothing, Y\in\mathscr{T}$.

	Suppose ${(V_{i})}_{i\in I}$ is an indexed family of elements of $\mathscr{T}$. Because the preimage of an arbitrary union is the union of preimages, it follows that $q^{-1}\left(\bigcup_{i\in I}V_{i}\right) = \bigcup_{i\in I}q^{-1}(V_{i})$. $q^{-1}(V_{i})$ is open in $X$ for every $i\in I$ so $q^{-1}\left(\bigcup_{i\in I}V_{i}\right)$ is open in $X$. Hence $\bigcup_{i\in I}V_{i}\in \mathscr{T}$.

	Suppose $V_{1}, \ldots, V_{n}\in \mathscr{T}$. Because the preimage of an arbitrary intersection is the intersection of preimages, we obtain $q^{-1}\left(\bigcap^{n}_{i=1}V_{i}\right) = \bigcap^{n}_{i=1}q^{-1}(V_{i})$. $q^{-1}(V_{i})$ is open in $X$ for every $i=1,\ldots,n$, so $q^{-1}\left(\bigcap^{n}_{i=1}V_{i}\right)$ is open in $X$, which means $\bigcap^{n}_{i=1}V_{i}\in\mathscr{T}$.

	Thus $\mathscr{T}$ is a topology on $Y$.
\end{proof}

\begin{exercise}{3.55}
	Show that every wedge sum of Hausdorff spaces is Hausdorff.
\end{exercise}

\begin{proof}
	Let ${(X_{\alpha})}_{\alpha\in A}$ be an indexed family of Hausdorff spaces. For each $\alpha\in A$, let $x_{\alpha}$ be a point of $X_{\alpha}$. Use these points as base points, we obtain the wedge sum $\bigvee_{\alpha\in A}X_{\alpha} = \left(\coprod_{\alpha\in A}X_{\alpha}\right)/\{ x_{\alpha} : \alpha\in A \}$. Let $q: \coprod_{\alpha\in A}X_{\alpha}\to \bigvee_{\alpha\in A}X_{\alpha}$ be the corresponding quotient map. Let $y, z$ be two distinct points of the wedge sum. Exactly one case of the following holds
	\begin{itemize}
		\item There is $X_{\alpha}$ such that $y = q(y'), z = q(z')\in q(X_{\alpha}\setminus\{ x_{\alpha} \})$. Because $X_{\alpha}$ is Hausdorff, there are disjoint neighborhoods $V_{y}, V_{z}$ of $y', z'$ in $X_{\alpha}$. $V_{y}\cap (X_{\alpha}\setminus\{ x_{\alpha} \}) = V_{y}\setminus\{ x_{\alpha} \}$ is also a neighborhood of $y'$, $V_{z}\setminus\{ x_{\alpha} \}$ is a neighborhood of $z'$. Hence $y, z$ are separated by neighborhoods $V_{y}\setminus\{ x_{\alpha} \}$ and $V_{z}\setminus\{ x_{\alpha} \}$ in the wedge sum.
		\item There are $i, j\in A$ where $i\ne j$ such that $y\in q(X_{i}\setminus\{ x_{i} \}), z\in q(X_{j}\setminus\{ y_{i} \})$. Then $y, z$ are separated by neighborhoods $X_{i}\setminus\{ x_{i} \}$ and $X_{j}\setminus\{ x_{j} \}$ in the wedge sum.
		\item $y = q(y')\in q(X_{\alpha}\setminus\{x_{\alpha}\})$ and $z = q(z')\in q({\{ x_{\alpha} \}}_{\alpha\in A})$. Because $X_{\alpha}$ is Hausdorff, $y', z'$ are separated by open sets $V_{y}, V_{z}$. Then $y, z$ are separated by $V_{y}$ and $V_{z}\amalg \coprod_{i\in A, i\ne\alpha}X_{i}$ (where $V_{z}\subseteq X_{\alpha}$) in the wedge sum.
	\end{itemize}

	Thus the wedge sum of Hausdorff spaces is Hausdorff.
\end{proof}

\subsection*{Recognizing Quotient Maps Between Known Spaces}\addcontentsline{toc}{subsection}{Recognizing Quotient Maps Between Known Spaces}

\begin{exercise}{3.59}\label{exercise:3.59}
	Let $q: X\to Y$ be any map. For a subset $U\subseteq X$, show that the following are equivalent
	\begin{enumerate}[label={(\alph*)}]
		\item $U$ is saturated.
		\item $U = q^{-1}(q(U))$.
		\item $U$ is a union of fibers.
		\item If $x\in U$, then every point $x'\in X$ such that $q(x) = q(x')$ is also in $U$.
	\end{enumerate}
\end{exercise}

\begin{proof}
	Suppose (a) is true, then there is a subset $V\subseteq Y$ such that $U = q^{-1}(V)$. Without loss of generality, we can assume that $V\subseteq q(X)$ (because adding points in $Y\setminus q(X)$ to $V$ doesn't change $q^{-1}(V)$). We always have $U\subseteq q^{-1}(q(U))$, so $q^{-1}(V)\subseteq q^{-1}(q(U))$, which implies $V\subseteq q(U)$. From $U = q^{-1}(V)$, it follows that $q(U) = q(q^{-1}(V))\subseteq V$. Hence $q(U) = V$, which means $U = q^{-1}(q(U))$. So (b) is true.

	Suppose (b) is true. Let $x\in U$ then $q(x)\in q(U)$. So $x\in q^{-1}(\{ q(x) \})\subseteq q^{-1}(q(U)) = U$, which implies every point of $U$ is contained in a fiber of $q$, which is again contained in $U$. Therefore $U$ is a union of fibers of $q$, so (c) is true.

	Suppose (c) is true. If $x\in U$ and $x'\in X$ such that $q(x) = q(x')$, then $x'\in q^{-1}(\{q(x)\})$, which is a fiber of $q$ contained in $U$. Therefore $x'$ is also in $U$, so (d) is true.

	Suppose (d) is true. If $x\in U$, then $x\in q^{-1}(\{ q(x) \})\subseteq U$, which means
	\[
		U = \bigcup_{x\in U}q^{-1}(\{ q(x) \}) = q^{-1}\left(\bigcup_{x\in U}\{ q(x) \}\right) = q^{-1}(q(U))
	\]

	which implies $U$ is saturated. So (a) is true.

	We showed that $(a)\implies (b) \implies (c) \implies (d) \implies (a)$, so (a), (b), (c), (d) are equivalent.
\end{proof}

\begin{exercise}{3.61}\label{exercise:3.61}
	Prove Proposition 3.60.

	A continuous surjective map $q: X\to Y$ is a quotient map if and only if it takes saturated open subsets to open subsets, or saturated closed subsets to closed subsets.
\end{exercise}

\begin{proof}
	$(\Rightarrow)$ Suppose $q$ is a quotient map.

	Let $U$ be a saturated subset of $X$. By Exercise~\ref{exercise:3.59}, $U = q^{-1}(q(U))$, moreover, preimages are well-behaved with set differences, so
	\[
		X\setminus U = X\setminus q^{-1}(q(U)) = q^{-1}(Y)\setminus q^{-1}(q(U)) = q^{-1}(Y\setminus q(U)).
	\]

	Because $q$ is a quotient map, $U$ is open if and only if $q(U)$ is open. Also because of this, $X\setminus U$ is open if and only if $Y\setminus q(U)$ is open, which means $U$ is closed if and only if $q(U)$ is closed. Hence $q$ takes saturated open subsets to open subsets, saturated closed subsets to closed subsets.

	$(\Leftarrow)$ Suppose $q$ takes saturated open subsets to open subsets.

	Let $V$ be a subset of $Y$ and $U = q^{-1}(V)$. If $U$ is open then $q(U) = q(q^{-1}(V)) = V$ (because $q$ is surjective) is open, because $q$ takes saturated open subsets to open subsets and $U$ is a saturated open subset of $X$. Conversely, if $V$ is open, then $U = q^{-1}(V)$ is open, because $q$ is continuous. Therefore $q$ is surjective, and $q^{-1}(V)$ is open if and only if $V$ is open, so $q$ is a quotient map.

	$(\Leftarrow)$ Suppose $q$ takes saturated closed subsets to closed subsets.

	Let $V$ be a subset of $Y$ and $U = q^{-1}(V)$, it follows that $X\setminus U = X\setminus q^{-1}(V) = q^{-1}(Y)\setminus q^{-1}(V) = q^{-1}(Y\setminus V)$. If $U$ is closed, then $q(U) = q(q^{-1}(V)) = V$ is closed, because $q$ takes saturated closed subsets to closed subsets and $U$ is a saturated closed set. If $V$ is closed, then $Y\setminus V$ is open and so is $X\setminus U = q^{-1}(Y\setminus V)$, from which we obtain $U$ is closed. Since $q$ is surjective, $q^{-1}(Y\setminus V)$ is open if and only if $Y\setminus V$ is open, it follows that $q$ is a quotient map.
\end{proof}

\begin{exercise}{3.63}
	Prove Proposition 3.62 (Properties of Quotient Maps).

	\begin{enumerate}[label={(\alph*)}]
		\item Any composition of quotient maps is a quotient map.
		\item An injective quotient map is a homeomorphism.
		\item If $q: X\to Y$ is a quotient map, a subset $K\subseteq Y$ is closed if and only if $q^{-1}(K)$ is closed in $X$.
		\item If $q: X\to Y$ is a quotient map and $U\subseteq X$ is a saturated open or closed subset, then the restriction $q\vert_{U}: U\to q(U)$ is a quotient map.
		\item If ${\{ q_{\alpha}: X_{\alpha}\to Y_{\alpha} \}}_{\alpha\in A}$ is an indexed family of quotient maps, then the map $q: \coprod_{\alpha}X_{\alpha} \to \coprod_{\alpha}Y_{\alpha}$ whose restriction to each $X_{\alpha}$ is equal to $q_{\alpha}$ is a quotient map.
	\end{enumerate}
\end{exercise}

\begin{proof}
	\begin{enumerate}[label={(\alph*)}]
		\item Let $q: X\to Y$ and $r: Y\to Z$ be quotient maps, then $q, r$ are surjective and continuous.

		      Because the composition of surjective maps is surjective, and composition of continuous map is continuous, it follows that $r\circ q$ is a continuous surjective map. Let $W$ be a subset of $Z$, we have ${(r\circ q)}^{-1}(W) = q^{-1}(r^{-1}(W))$.

		      If ${(r\circ q)}^{-1}(W)$ is open (it is also saturated), then $U = q^{-1}(r^{-1}(W))$ is open. By Exercise~\ref{exercise:3.61}, together with the surjectivity of $q, r$, we get $q(U) = r^{-1}(W)$ is a saturated open subset of $Y$, and $W = r(q(U))$ is an open subset of $Z$.

		      By Exercise~\ref{exercise:3.61}, we conclude that $r\circ q$ is a quotient map.
		\item Let $q: X\to Y$ be an injective quotient map.

		      Because a quotient map is surjective, it follows that $q$ is bijective. $q$ is continuous, which directly follows from the definition of quotient map. Because $q$ is bijective, $q^{-1}(q(U)) = U$ for every subset $U\subseteq X$, on the other hand $q$ is a quotient map, so $q(U)$ is open if and only if $U$ is open, which means $q$ is an open map. $q$ is bijective, continuous, and open, so $q$ is a homeomorphism.
		\item Because preimages are well-behaved with set differences, $X\setminus q^{-1}(K) = q^{-1}(Y)\setminus q^{-1}(K) = q^{-1}(Y\setminus K)$. Because $q$ is a quotient map, $Y\setminus K$ is open if and only if $q^{-1}(Y\setminus K) = X\setminus q^{-1}(K)$ is open. Therefore $q^{-1}(K)$ is closed if and only if $K$ is closed.
		\item The following proof implicitly uses subspace topologies.

		      Suppose $U\subseteq X$ is a saturated open subset, then $U = q^{-1}(q(U))$. The restriction $q\vert_{U}$ is still surjective and continuous. By Exercise~\ref{exercise:3.61}, $q(U)$ is open in $Y$. Let $W$ be a subset of $q(U)$.

		      If $W$ is open in $q(U)$, then it is also an open in $Y$. ${(q\vert_{U})}^{-1}(W) = q^{-1}(W)$ is open in $X$. Moreover, $q^{-1}(W)\subseteq q^{-1}(q(U)) = U$. Therefore $q^{-1}(W)$ is open in $U$.

		      If ${(q\vert_{U})}^{-1}(W)$ is open (it is also saturated), $(q\vert_{U})({(q\vert_{U})}^{-1}(W)) = (q\vert_{U})(q^{-1}(W)) = q(q^{-1}(W)) = W$ is open in $Y$. $q(U)$ is open in $Y$ and $W\subseteq q(U)\subseteq Y$ is open in $Y$, so $W$ is open in $q(U)$.

		      Suppose $U\subseteq X$ is a saturated closed subset. By Exercise~\ref{exercise:3.61}, $q(U)$ is closed in $Y$. Let $W$ be a subset of $q(U)$.

		      ${(q\vert_{U})}^{-1}(q(U)\setminus W) = U\setminus {(q\vert_{U})}^{-1}(W)$, so analogously $W$ is closed in $q(U)$ if and only if ${(q\vert_{U})}^{-1}(W) = q^{-1}(W)$ is closed in $U$.

		      Hence $q\vert_{U}: U\to q(U)$ is a quotient map.
		\item Let $(y, \alpha)$ be a point of $\coprod_{\alpha\in A}Y_{\alpha}$, then there is $x\in X_{\alpha}$ such that $q_{\alpha}(x) = y$. Therefore $q((x, \alpha)) = (y, \alpha)$, which implies that $q$ is surjective.

		      Let $V$ be a subset of $\coprod_{\alpha\in A}Y_{\alpha}$. We have
		      \[
			      V = \coprod_{\alpha\in A}(V\cap Y_{\alpha})
		      \]

		      and because preimages is well-behaved with arbitrary intersection and arbitrary unions,
		      \[
			      q^{-1}(V) = \coprod_{\alpha\in A}(q^{-1}(V)\cap X_{\alpha}) = \coprod_{\alpha\in A}(q^{-1}(V)\cap q^{-1}(Y_{\alpha})) = \coprod_{\alpha\in A}q^{-1}(V\cap Y_{\alpha}).
		      \]

		      If $V$ is open, then $q_{\alpha}^{-1}(V\cap Y_{\alpha})$ is open for every $\alpha\in A$, so $q^{-1}(V)$ is open in $\coprod_{\alpha\in A}X_{\alpha}$.

		      If $q^{-1}(V)$ is open, then $q^{-1}(V)\cap X_{\alpha} = q^{-1}(V)\cap q^{-1}(Y_{\alpha}) = q^{-1}(V\cap Y_{\alpha}) = q_{\alpha}^{-1}(V\cap Y_{\alpha})$ is open for every $\alpha\in A$. Because $q_{\alpha}$ is a quotient map, and $q_{\alpha}^{-1}(V\cap Y_{\alpha})$ is a saturated open subset of $X_{\alpha}$, it follows that $V\cap Y_{\alpha}$ is open in $Y_{\alpha}$ for every $\alpha\in A$. Therefore $V$ is open in $\coprod_{\alpha\in A}Y_{\alpha}$.

		      So $V$ is open in $\coprod_{\alpha\in A}Y_{\alpha}$ if and only if $q^{-1}(V)$ is open in $\coprod_{\alpha\in A}X_{\alpha}$. $q$ is also surjective, so $q$ is a quotient map.
	\end{enumerate}
\end{proof}

\subsection*{The Characteristic Property and Uniqueness}\addcontentsline{toc}{subsection}{The Characteristic Property and Uniqueness}

\begin{exercise}{3.72}
	Prove Theorem 3.71 (Uniqueness of the Quotient Topology).

	Given a topological space $X$, a set $Y$, and a surjective map $q: X \to Y$, the quotient topology is the only topology on $Y$ for which the characteristic property holds.
\end{exercise}

\begin{proof}
	Let $\mathscr{T}$ be the quotient topology on $Y$ induced by the map $q$, and $\mathscr{T}'$ be a topology on $Y$ for which the characteristic property holds. Let $\operatorname{Id}: Y\to Y'$ be the identity map, where $Y'$ is $Y$ with the topology $\mathscr{T}'$. The following diagram (see~\ref{fig:3.72}) commutes.
	\begin{figure}[htp]
		\renewcommand{\thefigure}{3.72}
		\centering
		\begin{tikzpicture}[every edge/.style={draw, -latex, thick}]
			\matrix (m) [matrix of math nodes, row sep=4em, column sep=4em] {
				X &    \\
				Y & Y' \\
			};

			\path[->] (m-1-1) edge node[left] {$q$} (m-2-1);
			\path[->] (m-1-1) edge node[above right] {$q$} (m-2-2);
			\path[->] (m-2-1) edge node[below] {$\operatorname{Id}$} (m-2-2);
		\end{tikzpicture}
		\caption{}\label{fig:3.72}
	\end{figure}

	By the characteristic property of the quotient topology, $q: X\to Y$ and $q: X\to Y'$ are continuous. On the other hand, $q = \operatorname{Id}\circ q$ and $q = \operatorname{Id}^{-1}\circ q$ are continuous. Also by the characteristic property, $\operatorname{Id}$ and $\operatorname{Id}^{-1}$ are continuous. Hence $Y$ and $Y'$ are homeomorphic, which implies the quotient topology is the only topology on $Y$ for which the characteristic property holds.
\end{proof}

\section*{Adjunction Spaces}\addcontentsline{toc}{section}{Adjunction Spaces}

No exercises.

\section*{Topological Groups and Group Actions}\addcontentsline{toc}{section}{Topological Groups and Group Actions}

\begin{exercise}{3.83}
	Verify that each of the above examples is a topological group.
\end{exercise}

\begin{proof}
	\begin{enumerate}[label={(\alph*)}]
		\item the real line $\mathbb{R}$ with its additive group structure and Euclidean topology

		      $m(x, y) = x + y$. Let $\openinterval{a, b}$ be a nonempty open interval of $\mathbb{R}$. We have
		      \[
			      m^{-1}(\openinterval{a,b}) = \bigcup_{a < c < b}\{ (x, y): x + y = c \}.
		      \]

		      Let $(x_{0}, y_{0})$ be a point of $m^{-1}(\openinterval{a,b})$ and $x_{0} + y_{0} = c$. Let $\delta = \min\left\{ \frac{c-a}{2}, \frac{b-c}{2} \right\}$. For every $(x, y)\in \openinterval{x_{0} - \delta, x_{0} + \delta}\times\openinterval{y_{0} - \delta, y_{0} + \delta}$,
		      \begin{align*}
			      x + y & < (x_{0} + y_{0}) + 2\delta = c + 2\delta \leq b \\
			      x + y & > (x_{0} + y_{0}) - 2\delta = c - 2\delta \geq a
		      \end{align*}

		      so the neighborhood $\openinterval{x_{0} - \delta, x_{0} + \delta}\times\openinterval{y_{0} - \delta, y_{0} + \delta}$ of $(x_{0}, y_{0})$ is contained in $m^{-1}(\openinterval{a, b})$. Hence $m^{-1}(\openinterval{a, b})$ is open in $\mathbb{R}\times\mathbb{R}$.

		      On the other hand, $i^{-1}(\openinterval{a, b}) = \openinterval{-b, -a}$, which is open in $\mathbb{R}$.

		      Let $U$ be an open subset of $\mathbb{R}$ then $U$ is an union of open intervals, so $m^{-1}(U)$ is open in $\mathbb{R}\times\mathbb{R}$, and $i^{-1}(U)$ is open in $\mathbb{R}$. Therefore $m, i$ are continuous, and it follows that the real line with the additive group structure and Euclidean topology is a topological group.
		\item the set $\mathbb{R}^{*} = \mathbb{R}\setminus\{0\}$ of nonzero real numbers under multiplication, with the Euclidean topology

		      First, we prove that $\cdot: \mathbb{R}\times\mathbb{R}\to\mathbb{R}$ is continuous. Let $(x_{0}, y_{0})\in\mathbb{R}\times\mathbb{R}$. For every $\varepsilon > 0$, let $\delta = -\frac{\abs{x_{0}}+\abs{y_{0}}}{2} + \sqrt{\varepsilon + {\left(\frac{\abs{x_{0}}+\abs{y_{0}}}{2}\right)}^{2}}$ then for every $(x, y)$ such that $\sqrt{{(x - x_{0})}^{2} + {(y - y_{0})}^{2}} < \delta$,
		      \begin{align*}
			      \abs{xy - x_{0}y_{0}} & = \abs{(x - x_{0})(y - y_{0}) + x_{0}(y - y_{0}) + y_{0}(x - x_{0})}                        \\
			                            & \leq \abs{(x - x_{0})(y - y_{0})} + \abs{x_{0}}\abs{y - y_{0}} + \abs{y_{0}}\abs{x - x_{0}} \\
			                            & \leq \frac{{(x - x_{0})}^{2} + {(y - y_{0})}^{2}}{2} + \delta(\abs{x_{0}} + \abs{y_{0}})    \\
			                            & < \delta^{2} + \delta(\abs{x_{0}} + \abs{y_{0}}) = \varepsilon
		      \end{align*}

		      Hence $\cdot: \mathbb{R}\times\mathbb{R}\to \mathbb{R}$ is continuous. Therefore $m: \mathbb{R}^{*}\times\mathbb{R}^{*}\to \mathbb{R}^{*}$ is also continuous.

		      A basis for the topology on $\mathbb{R}^{*}$ is the collection of open intervals of which endpoints are both positive, or negative.
		      \[
			      i^{-1}(\openinterval{a, b}) = \begin{cases}
				      \openinterval{\frac{1}{b}, \frac{1}{a}}   & \text{if $a, b > 0$} \\
				      \openinterval{\frac{-1}{a}, \frac{-1}{b}} & \text{if $a, b < 0$}
			      \end{cases}
		      \]

		      Hence $i: \mathbb{R}^{*}\to \mathbb{R}^{*}$ is continuous. Thus $\mathbb{R}^{*}$ under multiplication with the Euclidean topology is a topological group.
		\item the set $\mathbb{C}^{*} = \mathbb{C}\setminus\{0\}$ of nonzero complex numbers under complex multiplication, with the Euclidean topology

		      We will prove that $\cdot: \mathbb{C}\times\mathbb{C}\to\mathbb{C}$ is continuous.

		      Let $(z_{0}, w_{0})\in \mathbb{C}\times\mathbb{C}$. For every $\varepsilon > 0$, let $\delta = -\frac{\abs{z_{0}} + \abs{w_{0}}}{2} + \sqrt{\varepsilon + {\left(\frac{\abs{z_{0}} + \abs{w_{0}}}{2}\right)}^{2}}$, then for every $(z, w)\in B_{\delta}((z_{0}, w_{0}))$
		      \begin{align*}
			      \abs{zw - z_{0}w_{0}} & = \abs{(z - z_{0})(w - w_{0}) + z_{0}(w - w_{0}) + w_{0}(z - z_{0})}                                                                   \\
			                            & \leq \abs{(z - z_{0})(w - w_{0})} + \abs{z_{0}}\abs{w - w_{0}} + \abs{w_{0}}\abs{z - z_{0}}                                            \\
			                            & \leq \frac{\abs{z - z_{0}}^{2} + \abs{w - w_{0}}^{2}}{2} + (\abs{z_{0}} + \abs{w_{0}})\sqrt{\abs{z - z_{0}}^{2} + \abs{w - w_{0}}^{2}} \\
			                            & < \frac{\delta^{2}}{2} + \delta(\abs{z_{0}} + \abs{w_{0}})                                                                             \\
			                            & < \delta^{2} + \delta(\abs{z_{0}} + \abs{w_{0}}) = \varepsilon
		      \end{align*}

		      so $\cdot: \mathbb{C}\times\mathbb{C}\to\mathbb{C}$ is continuous. Hence $m: \mathbb{C}^{*}\times\mathbb{C}^{*}\to \mathbb{C}^{*}$ is continuous.

		      Let $z_{0}\in\mathbb{C}^{*}$ and $B_{\varepsilon}(1/z_{0})\subseteq \mathbb{C}^{*}$. Let $\delta = \frac{\varepsilon\abs{z_{0}}^{2}}{1 + \varepsilon\abs{z_{0}}}$, then for every $z\in B_{\delta}(z_{0})$, $\abs{z}\geq \abs{z_{0}} - \abs{z - z_{0}} > \abs{z_{0}} - \delta > 0$, and
		      \begin{align*}
			      \abs{i(z) - i(z_{0})} & = \abs{\frac{1}{z} - \frac{1}{z_{0}}}                            \\
			                            & = \frac{\abs{z - z_{0}}}{\abs{z}\abs{z_{0}}}                     \\
			                            & \leq \frac{\delta}{(\abs{z_{0}} - \abs{z - z_{0}})\abs{z_{0}}}   \\
			                            & < \frac{\delta}{(\abs{z_{0}} - \delta)\abs{z_{0}}} = \varepsilon
		      \end{align*}

		      so $i: \mathbb{C}^{*}\to \mathbb{C}^{*}$ is continuous. Thus $\mathbb{C}^{*}$ under multiplication with the Euclidean topology is a topological group.
		\item the general linear group $\operatorname{GL}(n, \mathbb{R})$, which is the set of $n\times n$ invertible real matrices under matrix multiplication, with the subspace topology obtained from $\mathbb{R}^{n^{2}}$ (where we identify an $n\times n$ matrix with a point in $\mathbb{R}^{n^{2}}$ by using the matrix entries as coordinates)

		      $\cdot: \mathbb{R}^{n^{2}}\times \mathbb{R}^{n^{2}}\to \mathbb{R}^{n^{2}}$ is a continuous map (because each entries of the product matrix is a polynomial of entries of the component matrices), so the restriction $m: \operatorname{GL}(n, \mathbb{R})\times\operatorname{GL}(n, \mathbb{R})\to \operatorname{GL}(n, \mathbb{R})$ is continuous.

		      $\det: \mathbb{R}^{n^{2}}\to \mathbb{R}$ defined by $\det A = \sum_{\sigma\in S_{n}}\operatorname{sign}(\sigma)A_{\sigma(1),1}\cdots A_{\sigma(n),n}$ is continuous, because $\det$ is the pointwise sum of continuous real-valued functions, namely, $A\mapsto \operatorname{sign}(\sigma)A_{\sigma(1),1}\cdots A_{\sigma(n),n}$, which are pointwise products of continuous real-valued functions. $\mathbb{R}\setminus\{0\}$ is open, so $\operatorname{GL}(n, \mathbb{R}) = \det^{-1}(\mathbb{R}\setminus\{0\})$ is open in $\mathbb{R}^{n^{2}}$. Consequently, the adjugate map $\operatorname{adj}: \mathbb{R}^{n^{2}}\to \mathbb{R}^{n^{2}}$ is also continuous (because entries of an adjugate matrix is defined by determinants).

		      Let $A\in \operatorname{GL}(n, \mathbb{R})$, then $i(A) = A^{-1} = \frac{1}{\det A}\operatorname{adj}A$. $A\mapsto \det A\mapsto 1/\det A$ is continuous, because $A$ is invertible and $\det$ is continuous, $\operatorname{adj}: \mathbb{R}^{n^{2}}\to \mathbb{R}^{n^{2}}$ is also continuous, so $i: \operatorname{GL}(n, \mathbb{R})\to \operatorname{GL}(n, \mathbb{R})$ is continuous.

		      Thus the real general linear group is a topological group.
		\item the complex general linear group $\operatorname{GL}(n, \mathbb{C})$, the set of $n\times n$ invertible complex matrices under matrix multiplication

		      The proof is similar to part (d).
		\item any group whatsoever, with the discrete topology (any such group is called a discrete group)

		      Let $G$ be a group with the discrete topology, then the product topology on $G\times G$ is also discrete, so $m: G\times G\to G$ is continuous. $G$ has the discrete topology, so $i: G\to G$ is also continuous. Hence every group with the discrete topology is a topological group.
	\end{enumerate}
\end{proof}

\begin{exercise}{3.85}
	Prove Proposition 3.84.

	Any subgroup of a topological group is a topological group with the subspace topology. Any finite product of topological groups is a topological group with the direct product group structure and the product topology.
\end{exercise}

\begin{proof}
	Let $H$ be a subgroup of the topological group $G$.

	$m: G\times G\to G$ is continuous, so $m\vert_{H\times H}: H\times H\to H$ is also continuous (the subspace topology and the product topology on $H\times H\subseteq G\times G$ are the same). $i: G\to G$ is continuous. Because $H$ is closure under multiplication, $i(H) = H$, and $i\vert_{H}: H\to H$ is also continuous. So $H$ with the subspace topology is a topological subgroup of $G$.

	Let $G_{1}, G_{2}, \ldots, G_{n}$ be topological groups. The following diagram (see~\ref{fig:3.85}) commutes.
	\begin{figure}[htp]
		\renewcommand{\thefigure}{3.85}
		\centering
		\begin{tikzpicture}[every edge/.style={draw,-latex,thick}]
			\matrix (m) [matrix of math nodes,row sep=3em,column sep=3em] {
				(G_{1}\times\cdots\times G_{n})\times (G_{1}\times\cdots\times G_{n}) & G_{1} \times\cdots\times G_{n} \\
				G_{i}\times G_{i}                                                     & G_{i}                          \\
			};
			\path[->] (m-1-1) edge[above] node {$m$} (m-1-2);
			\path[->] (m-1-1) edge[left] node {$f_{i}$} (m-2-1);
			\path[->] (m-1-2) edge[left] node {$\pi_{i}$} (m-2-2);
			\path[->] (m-2-1) edge[below] node {$m_{i}$} (m-2-2);
		\end{tikzpicture}
		\caption{}\label{fig:3.85}
	\end{figure}

	Define $f_{i}: (G_{1}\times\cdots\times G_{n})\times (G_{1}\times\cdots\times G_{n})\to G_{i}\times G_{i}$ for $i = 1, \ldots, n$ by
	\[
		f_{i}((a_{1}, \ldots, a_{n}), (b_{1}, \ldots, b_{n})) = (a_{i}, b_{i})
	\]

	$f_{i}$ is continuous, because the preimage of a product open set $B\times B'\subseteq G_{i}\times G_{i}$ is
	\[
		(G_{1}\times\cdots\times G_{i-1}\times B\times G_{i+1}\times\cdots\times G_{n})\times (G_{1}\times\cdots\times G_{i-1}\times B'\times G_{i+1}\times\cdots\times G_{n}).
	\]

	$m_{i}: G_{i}\times G_{i}\to G_{i}$ is the operation on $G_{i}$, which is continuous, for $i = 1, \ldots, n$. $\pi_{i}\circ m = m_{i}\circ f_{i}$ is continuous for $i = 1, \ldots, n$, so $m$ is continuous, by the characteristic property of the product topology. Hence $m$ is continuous.

	$i: G_{1}\times\cdots\times G_{n}\to G_{1}\times\cdots\times G_{n}$. Let $B_{1}\times\cdots\times B_{n}$ be a product open set in $G_{1}\times\cdots\times G_{n}$, then $i^{-1}(B_{1}\times\cdots\times B_{n}) = i_{1}^{-1}(B_{1})\times\cdots\times i_{n}^{-1}(B_{n})$, which is open because $i_{i}^{-1}(B_{i})\subseteq G_{i}$ is open for $i = 1,\ldots,n$, since $G_{i}$ is a topological group. Hence $i$ is continuous.

	Therefore $G_{1}\times\cdots\times G_{n}$ is a topological group. Thus the finite product of topological groups with the direct product and the product topology is a topological group.
\end{proof}

\subsection*{Group Actions}\addcontentsline{toc}{subsection}{Group Actions}

No exercises.

\section*{Problems}\addcontentsline{toc}{section}{Problems}

% Suppose ${(X_{\alpha})}_{\alpha\in A}$ is an indexed family of topological spaces and $Y$ is any topological space. A map $f: \coprod_{\alpha\in A}X_{\alpha}\to Y$ is continuous if and only if its restriction to each $X_{\alpha}$ is continuous. The disjoint union topology is the unique topology on $\coprod_{\alpha\in A}X_{\alpha}$ with this property.
